---
title: "Beautifull Visualization with ggplot"
author: "Tomas Castaño"
date: "29 de noviembre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hi everybody how are you? Today I come to present you with a very simple and beautiful way to present our selectable graphics.

To perform this exercise we need the following libraries: plotly and crosstalk.

```{r libraries}
library(plotly)
library(crosstalk)
```
First of all we load our dataset to be able to play with the data. In this case, it is the number of sales per store in a country.

```{r loadDAta}
Example <- read.csv("Example.csv")
Example <- Example[1:5,]
head(Example)
```


And here the code with a brief explanation:

```{r Example}
# Here we specify what the variable will be to select
Selectize <- SharedData$new(Example, ~Shop, "Select a Shop")
#In this place we created the graph
p <-  plot_ly(Selectize, color = ~Shop) %>%
  add_trace(x = ~Shop, y = ~Sales, type = 'bar',
             text = ~Sales, textposition = 'auto',
             marker = list(color = 'Shop',
                           line = list(color = 'rgb(8,48,107)', width = 1.5))) %>%
  layout(title = paste0("Sales by Shop"),
         barmode = 'group',
         xaxis = list(title = "Shop"),
         yaxis = list(title = "Sales"))
#Here we create the relationship between the selector and the graph
select <- highlight(
  ggplotly(p, tooltip = "Shop"), 
  selectize = TRUE, persistent = TRUE
)
#This helper function makes it easy to put HTML elements side by side.
bscols(select)
```

And as they can be we obtain a selectable graph that allows us to analyze the results in a visual way.
