---
title: "Connect to MySQL with R"
author: "Tomas Castaño"
date: "29 de noviembre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today i want to show you and example to connect Rstudio with MySQL server, for do that, yo will need the library RMySQL

```{r library}
library(RMySQL)
```

First of all, we need to create a conexion with the Database, for do that we need the user, password, db name and host.

```{r Conection}

MyDataBase = dbConnect(MySQL(), user='shipment_root', password='Dmz_5458', dbname='shipment', host='hostingmysql292.nominalia.com')
```

Ifwe want know the name of the tablesle voy a preguntar
in the data base we can use the function "dbListTables"

```{r dbListTables}

dbListTables(MyDataBase)
```

Once we know the tables, we can see what is inside of each one with "dbListFields".

```{r dbListTables2}

dbListFields(MyDataBase, 'wp_shipment_terms')

```

Now, we have connection with the database and using the function "dbGetQuery", we can get the data that we need.

```{r dbListTables3}

DataDB = dbGetQuery(MyDataBase, "select * from wp_shipment_terms")
head(DataDB)
```
