---
title: "ReadXlsxFiles"
author: "Tomas Castaño"
date: "22 de noviembre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## How to read a xlsx file in r with multipe Sheets?

Hi Everyone, today i want show you how to read a xlxs file in R, for use this function you must have the library readxl, so the first step is install the readxl library.


```{r library}
# Yo can download the library from cran or github devtools::install_github('dragua/xlsx')
#install.packages('readxl')
library(readxl)
```

If we want to read a xlxs, we can use the function "read_excel", for play with this function we need to pass two basic parameters basic: The file name and the Sheet that we want read.


```{r Example}
#We can use this method to read for example the sheet 1.( with numbers)
dataWithNumericSheet <- read_excel("example.xlsx", sheet = 1)
dataWithNumericSheet
# Or we can use this another method with string
dataWithStringSheet <- read_excel("example.xlsx", sheet = "Hoja 2")
dataWithStringSheet
```

Sometimes we have more of one sheet in a Excel document, and we need all the data of document, in this case we can create a easy solution..

```{r Example2}
# Using excel_sheets, we can get the names of sheets and create a list with them.
sheets <- readxl::excel_sheets("example.xlsx")
sheets <- as.list(sheets)

# When we have the list, we createa loop for each sheet and we save the data in the variable "finalData".

finalData <- data.frame()
for (i in 1:length(sheets)){
  if (nrow(finalData) == 0 ) {
    data <- read_excel("example.xlsx", sheet = sheets[[i]] )
    finalData <- data
  }else{
    dataNext <- read_excel("example.xlsx", sheet = sheets[[i]] )
    finalData <-  cbind(finalData,  dataNext)
  }
}
finalData

```

As you can see is very easy create a dataframe following our steps, if you have any problem to read excel documents write us and we will help you.

A hug

